---
title: "About Writing Dynamic Documents with R"
author:
- Author Name^1^
- ^1^Department of Geography, University of Zurich, Winterthurerstrasse 190, Zurich
- name@geo.uzh.ch
bibliography: bibliography.bib
output:
  pdf_document:
    keep_tex: yes
  html_document: default
  word_document:
    fig_caption: yes
    fig_width: 4
    reference_docx: template.docx
csl: springer-basic.csl
abstract: "This is the abstract of the template document used to show how to write
  \npublications in R with R Markdown and the help of some packages.  Based on a \nconcrete
  usecase this document exemplifies some of the caveats that may occur\nwhen writing
  such document and publish it online on a GIT repository. It also\npresents typical
  usecases in MarkDown usage and presents some tricks.\n     \n"
---

```{r setup,comment=FALSE, message = FALSE, echo=FALSE,warning=FALSE}
rm(list=ls())           # Clean the environment
options(scipen=6)       # display digits proberly!! not the scientific version
options(digits.secs=6)  # use milliseconds in Date/Time data types
options(warning=FALSE)  # don't show warnings
library(knitr)          # set global knitr options of the document
# Here we set the figure path to be in the figure folder and we also set the R code invisible to not show when the document is rendered
opts_chunk$set(comment="", message = FALSE, echo=FALSE, error=FALSE, warning=FALSE)
```

```{r directorySetup,comment=FALSE, message = FALSE, echo=FALSE,warning=FALSE}
dataFolder   <- file.path("data")   # Set path to the data and figure folder
figureFolder <- file.path("figures")
RFolder      <- file.path("R")      # Set the path to the RScript folder
# Load the R libraries
# install.packages(c("plyr","reshape2","ggmap","ggplot2","scales","rgdal","maptools","tools"),dependencies = TRUE)
l<-lapply(list("plyr","reshape2","ggmap","ggplot2","scales","rgdal","maptools","tools"), require, character.only = TRUE)
```

## Introduction 

This example publication is aimed to serve as a motivation on how to create reproducible documents in R and to advocate in general reproducible research.

## State of the Art

Various authors in qualitative and quantitive research argue for that as many parts of the research workflow reproducible. @Brunsdon2015 state "Reproducible quantitative research is research that has been documented sufficiently rigorously that a third party can replicate any quantitative results that arise". 

To further motivate you, read [@Healy2016,@Leveque2012,@Baker2016,@Nature2016,@Pebesma2012,@Vandewalle2012,@Nuest2011,@Buckheit1995,@Healy2011] or the short and to the point editorial of @Nature2016.

## Case Study - Parc Adula

This case study presents a small subset of a current study conducted at the Department of Geography at the University of Zurich. The study investigates the development of a second Swiss National Park, the _Adula Parc_. 

### Exploratory topic analysis

For this case study 16 interviews have been carried out. Each of these guided interviews got annotated based on a predefined topic tree. The following plots displays a sample of an output from MXAQDA as software for qualitative data analysis.

Overview on the held interviews and representants:

* _Cantonal Goverment_ (n: 4): Representants of four different involved departments
* _Environmental Organisation_ (n: 1): Involved as a stackholder in the park planning
* _Federal Goverment_ (n: 2): Responsible that the parc follows regulations of 'Natur- und Heimatschutz'
* _Local_ (n: 5): Local representants of the park region
* _Parc Team_ (n: 2 ): Team member involved in the park planning
* _Tourism_ (n: 2): Local tourism representants


The following plot presents the frequency of occurence of a select list of topics that occured in the interviews. While there seem to be spent more focus on the _Pro Argument_ against the _Contra Argument_ during the interviews. It is interesting to see that comparing topics on _Tourismus_ have far more weight than those on _Biodiversität_.

```{r read}
d <- read.csv(file.path(dataFolder,"interview_data.csv"),sep=";",stringsAsFactors = FALSE)
names(d) <- gsub("[.]"," ", names(d))
d <- cbind(d[,1:4],d[ , order(names(d[,5:ncol(d)]),decreasing = TRUE)+4]) # column order hack
d <- ddply(d, .(ParentCode), numcolwise(sum)) # summarise variable
d.m <- melt(d)
```

```{r tableTopics}
ds <-data.frame(Code=d$ParentCode,Mention=rowSums(d[,2:ncol(d)]))
knitr::kable(ds, caption = "Topic mentions.")
```

Figure presents the frequences matrix of the topics occurences across the different interviews. It provides an overview on where and by which representant topics occur.

```{r plotfreq,fig.height=4,fig.width=6,fig.cap="Frequency matrix of a selected list of topics across the various representants"}
p <- ggplot(d.m, aes(x=ParentCode,variable)) + geom_tile(aes(fill = value), colour = "white") + scale_fill_gradient(low = "white", high = "steelblue")
p <- p + theme_bw()  + labs(x = "Topic",y = "Participants", title="Frequency of topic occurences") + theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, colour = "grey50"))+ scale_x_discrete(expand = c(0, 0))+ guides(fill=guide_legend(title="Topic \nfrequencies"))
p
```

**Notes on reproducibility:** Depending on the data to analize privacy plays a role. While for the analysis itself the data is being anonymised, storing the raw or preprocessed data on a public repository may poses issues regarding the privacy of the data.

### Google query timeline

```{r readGoogleTrend}
# https://www.google.com/trends/explore?date=all&q=parc%20adula
d <- read.csv(file.path(dataFolder,"google_trend.csv"),sep=",",stringsAsFactors = FALSE,skip = 2)
names(d)<- c("Month","Count")
d$Month <- as.Date(paste(d$Month,"-01",sep=""))
# keep only the queries after March 2007, seems that before the counting is weird..
d<-d[d$Month>as.Date("2007-03-01"),]
```

Overview on the Google trend evolution on the search query: _Parc Adula_ ([url](https://www.google.com/trends/explore?date=all&q=parc%20adula), provides a CSV file). The timeline shows overall a small amount of queries for this word combination, with a spike on `r d[which.max(d$Count),"Month"]`. The has been retrieved on August 11, 2016.


**Notes on reproducibility:** API are subject to license restrictions, consider them carefully before using them in a scientific project. You may also consider store the raw on a local repository, for instance for cases where the services seizes to exist or the data is subject to change based on when you query it.


```{r googleTrend,fig.height=2,fig.width=5,fig.cap="Timeline of queries for Parc Adula set in the Google search engine"}
ggplot( d, aes(Month, Count)) + geom_line() +labs(list(x = "", y = "Monthly Queries", title ="Google Trend queries for 'Parc Adula'"))+theme_bw()
```


### Case study area

Parc Adula is situated in Switzerland in the border region of the cantons Ticino and Grisons. The map below presents the current outer perimiter of the planned national parc.


**Notes on reproducibility:** Due to license restrictions of the open geodata it is not possible to store the data on a public Git repository. The included script `R/loadMapData.r` downloads the data directly from the link provided in the geodata catalog infobox of http://maps.geo.admin.ch


```{r map,fig.width=4, out.width = "60%",fig.cap="Planned perimeter of Parc Adula, Switzerland, Data source: Swisstopo"}
# Download and extract Shapefiles from geo.admin.ch
# Due to license restrictions, we can't store the data on a public Git repository.
# https://map.geo.admin.ch/?topic=ech&lang=de&bgLayer=ch.swisstopo.pixelkarte-farbe&catalogNodes=458,532,639,653&layers=ch.swisstopo.swissboundaries3d-land-flaeche.fill,ch.swisstopo.swissboundaries3d-kanton-flaeche.fill,ch.bafu.schutzgebiete-paerke_nationaler_bedeutung&X=190000.00&Y=662000.00&zoom=1&layers_opacity=1,1,0.85

# Create the map if the map images does not exist
mapPng <- file.path(figureFolder,"map.png")
if(!file.exists(mapPng)){
  # the map generation code is stored in an external R script to increase the 
  # readibility of this Rmd file
  source(file.path(RFolder,"loadMapData.r"))
}else{knitr::include_graphics(mapPng)}
```

## Discussion &  Conclusions

This template based on data of an ongoing research project presents some typical examples maybe used in a publication writen in RMarkdown. It presents the inclusion of data and analysis, features plots, tables, and various markdown elements and shows how to integrate literature. The generated files in _PDF_, _Word_ or _HTML_ often still need fine some fine-tuning afterwards (particularly in Latex). However, it still presents a great way documenting the research process, that is easily shareable and the generation of the initial drafts.

# Acknowledgements

The Reproducible Research workshop was supported by the InnoPool of the Department of Geography, University of Zurich.


```{r session_info, results='markup'}
# Session info (include it for your own reproducibility)
# devtools::session_info()
```

# References
